\titleformat{\section}{\Large\bfseries}{}{0pt}{\thesection.\quad}	% Customize section titles

\section{Introduction} \label{sec:intro}
\iftoggle{toclinks}{\gototoc}{} 				% Turn it on/off in packages.tex
\iftoggle{cboxes}{	   				  			% Turn it on/off in packages.tex
	\begin{boxeditems}
		\item To-do list.
	\end{boxeditems}}{}

Part I: Research question, Answer, Positioning of paper in the literature; the order may vary. Part II: Description of sections' takeaways. Length from 3 to 5 pages.

\iftoggle{fulldraft}{							% Turn it on/off in packages.tex

David Evans' approach for an introduction:\footnote{\url{https://www.cgdev.org/blog/how-write-introduction-your-development-economics-paper}}
\begin{singlespace}
	\vspace{-0.3cm}
	\begin{itemize}
		\item 1–2 paragraphs. Motivate with a question or problem.
		\item 1 paragraph. Clearly state your research question.
		\item 1 paragraph. Empirical approach.
		\item 3–4 paragraphs. Detailed results.
		\item 1–3 paragraphs. Value-added relative to related literature.
		\item Optional paragraphs: Robustness checks, policy relevance, limitations.
		\item 1 paragraph. Roadmap.
	\end{itemize}
\end{singlespace}

\textchange{For an example of a great introduction see \textcite{MankiwRomerWeil:1992QJE}.}

}{}												% Closes \iftoggle{fulldraft}


\section{Section} \label{sec:structure}
\iftoggle{toclinks}{\gototoc}{} 				% Turn it on/off in packages.tex
\iftoggle{cboxes}{	   				  			% Turn it on/off in packages.tex
	\begin{boxeditems}
		\item To-do list.
	\end{boxeditems}}{}

Section takeaway.

\iftoggle{fulldraft}{							% Turn it on/off in packages.tex
Section content (omitted from outline).

}{}												% Closes \iftoggle{fulldraft}

\subsection{Subsection}
\iftoggle{toclinks}{\gototoc}{} 				% Turn it on/off in packages.tex

Subsection takeaway.

\iftoggle{fulldraft}{							% Turn it on/off in packages.tex
Subsection content (omitted from outline).

}{}												% Closes \iftoggle{fulldraft}

\subsubsection{Sub-subsection}

Sub-subsection takeaway.

\iftoggle{fulldraft}{							% Turn it on/off in packages.tex
Sub-subsection content (omitted from outline).

}{}												% Closes \iftoggle{fulldraft}


\section{Examples} \label{sec:examples}
\iftoggle{toclinks}{\gototoc}{} 				% Turn it on/off in packages.tex
\iftoggle{cboxes}{	   				  			% Turn it on/off in packages.tex
	\begin{boxeditems}
		\item To-do list.
	\end{boxeditems}}{}

Section takeaway.

\iftoggle{fulldraft}{							% Turn it on/off in packages.tex
Cite figure \ref{fig:exfig}, table \ref{tab:extab} and (dynamic) numbers like \double{../Numbers/exNumMean.txt}. Omitted from outline.
	
\input{../Equations/exMultiOneN}
\input{../Equations/exMultiEachN}

\iftoggle{floatstxt}{
	\input{../Figures/exfig}
	}{
	\begin{center}
		[Insert Figure \ref{fig:exfig} Here.]
	\end{center}
}

\iftoggle{floatstxt}{
	\input{../Tables/extab}
	}{
	\begin{center}
		[Insert Table \ref{tab:extab} Here.]
	\end{center}
}


}{}												% Closes \iftoggle{fulldraft}


\section{Conclusions}\label{sec:conclusions}
\iftoggle{toclinks}{\gototoc}{} 				% Turn it on/off in packages.tex
\iftoggle{cboxes}{	   				 			% Turn it on/off in packages.tex
	\begin{boxeditems}
		\item To-do list.
	\end{boxeditems}}{}

Summary.

\iftoggle{fulldraft}{							% Turn it on/off in packages.tex
Remarks (omitted from outline).

}{}	% Closes \iftoggle{fulldraft}


\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}	% Restore section titles defaults


\iftoggle{fulldraft}{							% Turn it on/off in packages.tex
	\iftoggle{blind}{
	\section*{Acknowledgments}
	
	\input{thanks}
	}{}
}{}												% Closes \iftoggle{fulldraft}
